
 

Load the dataset into R as a dataframe.
```{r}

df <- read.csv("[Group 4]InterNOT.csv")

#Renaming the column names to $-accessible handles
colnames(df) <- c('ts','q1',	'q2',	'q3',	'q4',	'q5',	'q6',	'q7',	'q8',	'q9',	'q10')

###Converting the string values to likert numericals in l1..l5
###Normalizing the values in A1..A5
#A1
temp <- c("Very Engaged", "Engaged", "Neither engaged nor disengaged", "Disengaged", "Very disengaged")
likert <- 1:length(temp)
names(likert)<-temp
df$l1<-likert[df$q1]
df$A1<-df$l1/length(temp) * 5
#A2
temp <- c("Very frequently","Frequently","Occasionally","Rarely","Very rarely","Never")
likert <- 1:length(temp)
names(likert)<-temp
df$l2<-likert[df$q2]
df$A2<-df$l2/length(temp) * 5
#A3
temp <- c("Complete all of the readings on time", 
          "Complete more than half of the readings",
          "Complete less than half of the readings",
          "Did not do any of the readings")
likert <- 1:length(temp)
names(likert)<-temp
df$l3<-likert[df$q3]
df$A3<-df$l3/length(temp) * 5
#A4
temp <- c("Read all of the readings in detail and researched more about them",
          "Read all of the readings in detail",
          "Read almost every section",
          "Skimmed through the readings",
          "Did not do any of the readings")
likert <- 1:length(temp)
names(likert)<-temp
df$l4<-likert[df$q4]
df$A4<-df$l4/length(temp) * 5
#A5
temp <- c("Strongly agree","Agree","Neither agree nor disagree","Disagree","Strongly disagree")
likert <- 1:length(temp)
names(likert)<-temp
df$l5<-likert[df$q7]
df$A5<-df$l5/length(temp) * 5

#df[c('l1', 'l2', 'l3', 'l4', 'l5', 'A1', 'A2', 'A3', 'A4', 'A5')]
sum(is.na(df))
```


```{r}
#install.packages("psych")
library("psych")

#head(bfi)
#?bfi
#str(bfi)

head(df)
str(df)
```

Computing the average inter-item correlations for each item.

Step 1: 

```{r}

## We don't have missing values. All our questions were mandatory.

# Creating a new dataframe containing only those variables
#scale_df = bfi[, c("A1","A2", "A3", "A4", "A5")]
scale_df = df[, c("A1","A2", "A3", "A4")]

# [Error Check] Check the class of your variables
str(scale_df)

# [Error Check] Check you have encoded the missing values correctly
table(scale_df$A1)
table(scale_df$A2)
table(scale_df$A3)
table(scale_df$A4)
```
Step 2: Flipping any variables that are reverse-coded. 
```{r}

## WE DO NOT HAVE ANY REVERSE-CODED QUESTIONS

### car was not installed before
#install.packages("car")
library(car)

# Reverse-coding A1

# The following is a quicker way to do multiple recodes using a specialized recode function. 

# You can also use the method we outline in the R tutorial and class session using indexing. 
#scale_df$recode_A1 = car::recode(scale_df$A1, "1=6; 2=5; 3=4; 4=3; 5=2; 6=1")

# [Error Check] Check the recode has been done correctly
#head(scale_df[, c("A1", "recode_A1")], 10)

```

Step 3: Running the correlation matrix.  
```{r}
scale_df2 = scale_df[, c("A1", "A2", "A3", "A4")]
cor(x=scale_df2, use = "pairwise.complete.obs")
```

Step 4: Computing the average inter-item correlation for each item.

```{r}
# You can assign the output of the cor function to a variable 
corr_matrix = cor(x=scale_df2, use = "pairwise.complete.obs")

# [Error check] Check the class of the function output (is a matrix). 
class(corr_matrix)

# Similar to dataframes, you can select the elements you want from the matrix, and feed it into the mean function to get your average inter-item correlation 

# Make sure you exclude the correlation of the variable with itself, as you select the elements to compute each inter-item correlation. 

A1_corrs = corr_matrix[1 , c(2,3,4)]

# [Error check] Double-check to make sure you've selected the elements of each matrix correctly. 
A1_corrs
corr_matrix

# [Error check]
is.vector(A1_corrs)
class(A1_corrs)

average_A1_corrs = mean(A1_corrs)
average_A1_corrs
## The inter-item correlation is 0.43 which is above 0.2 (yay!)
```

```{r}
#We did mean of inter-item correlation of each question.
mean(corr_matrix[1 , c(2,3,4)])
mean(corr_matrix[2 , c(1,3,4)])
mean(corr_matrix[3 , c(1,2,4)])
mean(corr_matrix[4 , c(1,2,3)])
```



##### Calculating Cronbach’s alpha for your set of likert-style variables. 

```{r}
psych::alpha(scale_df2[, c("A1", "A2", "A3", "A4")], check.keys=TRUE)

##Our raw alpha value is 0.76
```

We get a (raw_alpha) value of 0.76 in our data. 

##### Creating a new scale which is the average of your likert-style variables. 

```{r}
library(car)
# Get the row mean of A1-A5. 
# The column index argument is unnecessary (since scale_df2 only has those 4 columns) but included for clarity. 
scale_df2$scale = rowMeans(scale_df2[, c("A1", "A2", "A3", "A4")], na.rm=TRUE)

# [Error check] Make sure the function does as expected - checking rows with NA values in particular. 
tail(scale_df2, 50)
```

#####  Plotting a histogram for each of your likert-style variables, and a histogram for your new scale (the average of your likert-style variables). Include these histograms in your lab pdf write-up, and briefly discuss and interpret any notable differences between the individual histograms and the histogram of your new scale.  

```{r}
hist(scale_df2$A1)
hist(scale_df2$A2)
hist(scale_df2$A3)
hist(scale_df2$A4)

# Increasing the number of breaks allows you to see more of the granularity in your new scale variable.  
hist(scale_df2$scale, breaks=24)
```
